---
title: "exam2"
author: "Rachel Rosenberg"
date: "6/26/2020"
output: pdf_document 
---
Set working directory
```{r}
setwd("/Users/racheleryn/Documents/Git/Exam2")
```

**Question 1**: Clear environment
```{r}
rm(list = ls())
```
**Question 2**: Load inequality data set
```{r}
library(rio)
inquality_data = import("inequality.xlsx", which = 1) # first tab
```
**Question 3**:
This data is not cross-sectional, it only shows countries in the year 2015. 
```{r}
library(dplyr)
glimpse(inquality_data)
```

**Question 4**: Subset the data (come back)
```{r}
subset(inquality_data, country == "Denmark")
subset(inquality_data, country == "Sweden")
```
**Question 5**: Subset the inequality_gni for Brazil (come back)
```{r}
subset(inquality_data, country == "Brazil")
```
**Question 6**:

Based on the previous results, it's better for `inequality_gni` to have a lower score. See the data below. (Return)

**Question 7**: View the head of the data frame
```{r}
head(inquality_data)
```
**Question 8**: write a function
```{r}
accent.remove = function(s) {
  old1 <- "ú"
  new1 <- "u"
  s1 <- chartr(old1, new1, s)
  for(i in seq_along(old1)) s1 <- gsub(old1[i], new1[i], s1, fixed = TRUE)
  s1
}

```
A view of the data with the accents removed (come back)
```{r}
head(inquality_data)
```
**Question 9**: Sort countries by lowest GNI values (come back)
```{r}
inquality_data = inquality_data[order(inquality_data$inequality_gini),]
```
A view of the newly sorted data
```{r}
head(inquality_data)
```
**Question 9**: Mean inequality_gni score (come back)
```{r}
mean(inquality_data$inequality_gini, na.rm = TRUE)
```
The mean of the score is `mean(inquality_data$inequality_gini, na.rm = TRUE)` (come back)

**Question 10**: create dummy variables (come back and use ifelse)
```{r}
inquality_data$high_inequality = NA
inquality_data$high_inequality[inquality_data$inequality_gini>36.81375] = 1
inquality_data$high_inequality[inquality_data$inequality_gini<36.81375] = 0

inquality_data$low_inequality = NA
inquality_data$low_inequality[inquality_data$inequality_gini<36.81375] = 1
inquality_data$low_inequality[inquality_data$inequality_gini>36.81375] = 0

```
**Question 11**: Run a cross tabulation
```{r}
library(doBy)
summaryBy(high_inequality ~ low_inequality, data = inquality_data, FUN=c(mean))
```
**Question 13** a for loop
```{r}
orgs <- c('World Bank', 'African Development Bank', 'Bill and Melinda Gates Foundation') 
for ( i in orgs){
print(i) }
```
**Question 15**: Variable 
I picked Central government debt, total (% of GDP). Highly indebted countries normally suffer from income inequality.

Question 16: Import variable from WB
```{r}
library(WDI)
debt_data = WDI(country = "all",
                indicator =c("GC.DOD.TOTL.GD.ZS"),
                start = 2015, end = 2015, extra = FALSE, cache = NULL)
```

Question?: Rename variable
```{r}
 library(data.table) 
setnames(debt_data,"GC.DOD.TOTL.GD.ZS", "Government % of Debt")
```
Question?: Merge data






